Measuring contrast processing in the visual system using SSVEP

### 2024-04-25 review.qmd
Attention

where $C_\mathrm{mask}$ reflects the contrast of the mask component at a distinct frequency from that of the target. The effect of this extra term is to reduce the target response (see right panel of @fig-twoinputs). For a linear contrast axis, the contrast response function becomes shallower, whereas on a logarithmic contrast axis it maintains its steepness and shifts to the right. Suppressive effects of this kind have been obtained using SSVEP with a variety of different types of mask, including orthogonal overlaid masks, surround masks, and dichoptic masks [for a meta-analysis see @Baker2021].

>>>>

where $C_\mathrm{mask}$ reflects the contrast of the mask component at a distinct frequency from that of the target. The effect of this extra term is to reduce the target response (see right panel of @fig-twoinputs). For a linear contrast axis, the contrast response function becomes shallower, whereas on a logarithmic contrast axis it maintains its steepness and shifts to the right. Suppressive effects of this kind have been obtained using SSVEP with a variety of different types of mask, including orthogonal overlaid masks, surround masks, and dichoptic masks (Burr and Morrone 1987; Ross and Speed 1991, Candy, Norcia, Busse, [@salelkar2020interaction] [for a meta-analysis see @cunningham2017NonLinear, @Baker2021].
